---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fedeconseries

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/harrysun26/fedeconseries.svg?branch=master)](https://travis-ci.org/harrysun26/fedeconseries)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/harrysun26/fedeconseries?branch=master&svg=true)](https://ci.appveyor.com/project/harrysun26/fedeconseries)
[![Codecov test coverage](https://codecov.io/gh/harrysun26/fedeconseries/branch/master/graph/badge.svg)](https://codecov.io/gh/harrysun26/fedeconseries?branch=master)
<!-- badges: end -->

The goal of fedeconseries is to obtain US federal reserve economc data.  Reserach use only.

## Installation

You can install the released version of fedeconseries from github with:

```r
#install.packages("fedeconseries")
library(devtools)
install_github("harrysun26/fedeconseries")
```

## Usage
A more detailed example can be found in my vignette: 


### Terms of use

When using the FRED&copy; API, you are agreeing to be bound by the FRED&copy; API Terms of Use, see https://research.stlouisfed.org/docs/api/terms_of_use.html.

## History
- 02.02.2020: Version 1.0 release

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(fedeconseries)
## basic example code
```

