---
title: "th Vignettes of fedeconseries"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{the_Vignettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

An easy way to download ALFRED data (US Frderal Reserve Economic data).

## Installation

You may install the last stable release , the latest development version from github.


```{r}
# install.packages("fedeconseries")
# or---
# install.packages("devtools")
# devtools::install_github("harrysun26/fedeconseries")

```

## Usage

Downloading data is straightforward (for real-time data from ALFRED see below):


```{r}
library(fedeconseries)
df <- get_fred_series2("INDPRO", "indpro")
```

The output is a data frame

```{r}
head(df)
```

This can be readily used, i.e. for plotting

```{r, fig.show = "hold"}
library(ggplot2)
ggplot(df) +
  geom_line(aes(x = date, y = indpro))
```

## Vintage data

When using get_fedeconseries for downloading real-time data sets, there will be an additional column for the respective vintage dates.

```{r}
df_vintages <-
  get_fedeconseries("GDPC1", "rgdp",
                    obs_start = "2007-05-31",
                    real_start = "2008-05-31", real_end = "2009-03-30")
head(df_vintages)
```

Because of its output being a tidy data frame, it is easy to visualise revisions by

```{r, fig.show = "hold", fig.width = 6}
library(ggplot2)

ggplot(df_vintages) +
  geom_line(aes(x = date, y = rgdp, colour = as.factor(realtime_period))) +
  theme_bw() +
  theme(
    legend.title = element_blank(),
    legend.position = "bottom"
  )
```
