---
title: "Detailed usage of library fedeconseries"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{the_Vignettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

An easy way to download clean ALFRED data (US Frderal Reserve Economic Series data--St.Louis Fed).

## Installation

You may install the last stable release , the latest development version from github.


```{r}
# install.packages("fedeconseries")
# or(if CRAN not working)---
# install.packages("devtools")
# library(devtools)
# devtools::install_github("harrysun26/fedeconseries")

```

## functions overview: 


* 
`search_fedeconseries("unemployment", search_type = 'full_text',realtime_start = NULL, realtime_end = NULL)`

  This function returns the unique identifier(economic variable in database) used in following functions `get_econ_series` and `get_fedeconseries`. Here, we pass keyword "unemployment" into function. 

*
  `get_econ_series("INDPRO", "indpro", observation_start = "2009-03-01", observation_end = "2009-03-01")`

  This function returns real value(raw data) of economic series.  No adjustments. Here we pass "INDPRO" as keyword and "indpro" as a rename, with observation start and end date. 

*                   
`get_fedeconseries("UNRATE", "unemployment",observation_start = "2013-03-01", observation_end = "2013-03-30",realtime_start = "2015-02-02", realtime_end = "2015-02-02")`
                  
  This function looks up unemployment data of US, with varying available date adjustment. Here we pass the keyword "UNRATE", rename as "unemployment", with observation start and end date, and research (real) start and end date. 


## Usage:

First, when use this package to fetch data from \url{https://alfred.stlouisfed.org}, you need to know the `s_id` which is the data identifier(anmely the economic variable name in website database). If you don't know the series_id, you could try `search_fedeconseries` to search some keywords. Say you want to know the "unemployment", but you do not the series identifier. Here is whay you could do:

```{r}
library(fedeconseries)
df <- search_fedeconseries("unemployment")
##for display purpose, I omited the 16th column, since it contains long notes.
head(df[,-16])
```

From the above dataframe, you could check the title, the frequency, the popularity, the notes, etc., then you could easily choose which one is what you need. Let's do with the first id from the first column: "UNRATE".

To download the data, use function :


```{r}
library(fedeconseries)
df <- get_econ_series("UNRATE","unemployment")
```

The output is a data frame

```{r}
head(df)
tail(df)
```

This can be readily used, i.e. for plotting

```{r, fig.show = "hold"}
library(ggplot2)
ggplot(df) +
  geom_line(aes(x = date, y = unemployment))
```

## Advanced search for historical data: Seasonal adjustments

When using get_fedeconseries for downloading real-time data sets, there will be an additional column for the respective vintage dates.

```{r}
df_vintages <-
  get_fedeconseries("UNRATE", "unemploymentRate",
                    obs_start = "2000-01-01",
                    real_start = "2019-05-01")
df_vintages
```

Because of its output being a tidy data frame, it is easy to visualise revisions by

```{r, fig.show = "hold", fig.width = 6}
library(ggplot2)

ggplot(df_vintages) +
  geom_line(aes(x = date, y = unemploymentRate, colour = as.factor(realtime_period))) +
  theme_bw() +
  theme(
    legend.title = element_blank(),
    legend.position = "bottom"
  )
```
